{\setlength{\baselineskip}{.7\baselineskip}
  {\scriptsize\noindent\DocID{} \textcopyright~\today{}, Exar{\tiny$^{\textregistered}$}{}, Inc.   
  All rights reserved.\hfill\textcolor{lightgray}{\currenttime}\\[.5ex]}

  {\scriptsize\noindent{}No part of this publication may be reproduced, transmitted,
  transcribed, stored in a retrieval system, or translated into any
  language in any form by any means without the written permission of
  Exar Corporation.}\\[.5ex]

  \noindent{\small\textbf{\textcolor{ThemeColor}{Licensing and Government Use}}}\\[.5ex]

  {\scriptsize\noindent{}Any Exar software (“Licensed Programs”) based on Hifn Technology
    described in this document is furnished under a license and may be
    used and copied only in accordance with the terms of such license and
    with the inclusion of this copyright notice. Distribution of this
    document or any copies thereof and the ability to transfer title or
    ownership of this document’s contents are subject to the terms of such
    license.}\\[.5ex]

    {\scriptsize\noindent{}Such Licensed Programs and their documentation may contain public
    open-source software that would be licensed under open-source
    licenses.  Refer to the applicable product release notes for
    open-source licenses and proprietary notices.  Use, duplication,
    disclosure, and acquisition by the U.S. Government of such Licensed
    Programs are subject to the terms and definitions of their applicable
    license.}\\[.5ex]

  \noindent{\small\textbf{\textcolor{ThemeColor}{Disclaimer}}}\\[.5ex]

  {\scriptsize\noindent{}Exar reserves the right to make changes to its products, including the
  contents of this document, or to discontinue any product or service
  without notice. Exar advises its customers to obtain the latest
  version of relevant information to verify, before placing orders, that
  information being relied upon is current. Every effort has been made
  to keep the information in this document current and accurate as of
  the date of this document’s publication or revision.}\\[.5ex]

  \noindent{\small\textbf{\textcolor{ThemeColor}{Limited Warranty}}}\\[.5ex]

  {\scriptsize\noindent{}Exar warrants Products based on the Hifn Technology, including cards,
  against defects in materials and workmanship for a period of twelve
  (12) months from the delivery date. Exar's sole liability shall be
  limited to either, replacing, repairing or issuing credit, at its
  option, for the Product if it has been paid for.  Exar will not be
  liable under this provision unless: (a)Exar is promptly notified in
  writing upon discovery of claimed defects by Buyer; (b)The claimed
  defective Product is returned to Exar, insurance and transportation
  charges prepaid, by Buyer; (c)The claimed defective Product is
  received within twelve (12) months from the delivery date; and
  (d)Exar's examination of the Product discloses to its satisfaction
  that the alleged defect was not caused by misuse, neglect, improper
  installation, repair, alteration, accident or other hazard. THIS
  WARRANTY DOES NOT COVER PRODUCT DAMAGE WHICH RESULTS FROM ACCIDENT,
  MISUSE, ABUSE, IMPROPER LINE VOLTAGE, FIRE, FLOOD, LIGHTNING OR OTHER
  ACTS OF GOD OR DAMAGE RESULTING FROM ANY MODIFICATIONS, REPAIRS OR
  ALTERATIONS PERFORMED OTHER THAN BY EXAR OR EXAR'S AUTHORIZED AGENT OR
  RESULTING FROM FAILURE TO STRICTLY COMPLY WITH EXAR'S WRITTEN
  OPERATING AND MAINTENANCE INSTRUCTIONS.  BUYER ACKNOWLEDGES THAT THE
  PRODUCT IS HIGHLY SENSITIVE ELECTRONIC PRODUCT REQUIRING SPECIAL
  HANDLING AND THAT THIS WARRANTY DOES NOT APPLY TO IMPROPERLY HANDLED
  PRODUCT.  PRODUCT MANUFACTURED TO MEET BUYER'S SPECIFIC PERFORMANCE
  SPECIFICATIONS ACCEPTED BY EXAR ARE WARRANTED ONLY TO PERFORM IN
  CONFORMITY WITH SUCH SPECIFICATIONS, AND ARE WARRANTED ONLY AGAINST
  DEFECTS NOT RELATED TO SUCH SPECIFICATIONS IN ACCORDANCE WITH THE
  TERMS AND CONDITIONS SET FORTH HEREIN ABOVE."}\\[.5ex]

  \noindent{\small\textbf{\textcolor{ThemeColor}{Life Support Policy}}}\\[.5ex]

  {\scriptsize\noindent{}Exar's Product is not authorized for use as critical components in
  life support devices or systems.  Life support devices or systems are
  devices or systems which, (a) are intended for surgical implant into
  the body, or (b) support or sustain life, and whose failure to
  perform, when properly used in accordance with instructions for use
  provided in the labeling, can be reasonably expected to result in a
  significant injury or death to human life. A critical component is any
  component of a life support device or system whose failure to perform
  can be reasonably expected to cause the failure of the life support
  device or system, or to affect its safety or effectiveness.  Buyer
  agrees to indemnify, defend and hold Exar harmless for any cost, loss,
  liability, or expense (including without limitation attorneys' fees
  and other costs of litigation or threatened litigation) arising out of
  violation of the above prohibition by Buyer or any person or entity
  receiving Exar's Product through Buyer.}\\[.5ex]

  \noindent{\small\textbf{\textcolor{ThemeColor}{Patent Infringement - Indemnification}}}\\[.5ex]

  {\scriptsize\noindent{}Exar agrees, at its own expense, to defend Buyer from and against any
  claim, suit or proceeding, and to pay all judgments and costs finally
  awarded against Buyer by reason of claim, suit or proceeding insofar
  as it is based upon an allegation that the Product as furnished by
  Exar infringes any United States letter patent, provided that Exar is
  notified promptly of such claim in writing and is given authority and
  full and proper information and assistance (at Exar's expense) for
  defense of same.  In case such Product are finally constituted an
  infringement and the use of Product is enjoined, Exar shall at its
  sole discretion and at its own expense: (1) procure for Buyer the
  right to continue using the Product; (2) replace or modify the same so
  that it becomes non-infringing; or (3) remove such Product and grant
  Buyer a credit for the depreciated value of the same.}\\[.5ex]

  {\scriptsize\noindent{}Buyer shall have the right to employ separate counsel in any claim,
  suit or proceeding and to participate in the defense thereof, but the
  fees and expenses of Buyer's counsel shall not be borne by Exar
  unless: (1) Exar specifically so agrees; or (2) Exar, after written
  request and without cause, does not assume such defense.  Exar shall
  not be liable to indemnify Buyer for any settlement effected without
  Exar's written consent, unless Exar failed, after notice and without
  cause, to defend such claim, suit or proceeding.  The indemnification
  shall not apply and Buyer shall indemnify Exar and hold it harmless
  from all liability or expense (including costs of suit and attorney's
  fees) if the infringement arises from, or is based upon Exar's
  compliance with particular requirements of Buyer or Buyer's customer
  that differ from Exar's standard specifications (Custom Product) for
  the Product, or modifications or alterations of the Product, or a
  combination of the Product with other items not furnished or
  manufactured by Exar.  Buyer agrees that Exar shall not be liable for
  any collateral, incidental or consequential damages arising out of
  patent infringement.  The foregoing states the entire liability of
  Exar for patent infringement."}\\[.5ex]

  \pagebreak
  \noindent{\small\textbf{\textcolor{ThemeColor}{Motorola}}}\\[.5ex]

  {\scriptsize\noindent{}The use of this product in stateful compression protocols (for
  example, PPP or multi-history applications) with certain
  configurations may require a license from Motorola. In such cases, a
  license agreement for the right to use Motorola patents (US05,245,614,
  US05,130,993) may be obtained directly from Motorola.}\\[.5ex]

  \noindent{\small\textbf{\textcolor{ThemeColor}{Patents}}}\\[.5ex]

  {\scriptsize\noindent{}May include one or more of the following United States patents:
  4,930,142; 4,996,690; 4,701,745; 5,003,307; 5,016,009; 5,126,739;
  5,146,221; 5,414,425; 5,414,850; 5,463,390; 5,506,580; 5,532,694;
  6,320,846; 6,816,459; 6,651,099; 6,665,725; 6,771,646; 6,789,116;
  6,954,789; 6,839,751; 7,299,282; 7,260,558. Other patents pending.}\\[.5ex]

  \noindent{\small\textbf{\textcolor{ThemeColor}{Trademarks}}}\\[.5ex]

  {\scriptsize\noindent{}Hi/fn{\tiny$^{\textregistered}$}, MeterFlow{\tiny$^{\textregistered}$},
  MeterWorks{\tiny$^{\textregistered}$}, and LZS{\tiny$^{\textregistered}$}, are registered
  trademarks of Exar Corporation. HifnTM, Hifn Technology,
  FlowThroughTM, BitWackr, and the Hifn logo are trademarks of Hi/fn,
  Inc. All other trademarks and trade names are the property of their
  respective holders.}\\[.5ex]

  {\scriptsize\noindent{}IBM, IBM Logo, and IBM PowerPC are trademarks of
  International Business Machines Corporation in the United States, or
  other countries.}\\[.5ex]

  {\scriptsize\noindent{}Microsoft, Windows, Windows XP, Windows Vista,
  Windows Server 2003, Windows Server 2008 and the Windows logo are
  trademarks of Microsoft Corporation in the United States, and/or other
  countries.  Intel QuickAssist is a trademark of Intel Corporation in
  the United States and in other countries.}\\[.5ex]

  \noindent{\small\textbf{\textcolor{ThemeColor}{Exporting}}}\\[.5ex]

  {\scriptsize\noindent{}This product may only be exported from the United States in accordance
  with applicable Export Administration Regulations. Diversion contrary
  to United States laws is prohibited.}\\[.5ex]

  \noindent{\small\textbf{\textcolor{ThemeColor}{Exar Confidential}}}\\[.5ex]

  {\scriptsize\noindent{}If you have signed an Exar Confidential Disclosure Agreement that
  includes this document as part of its subject matter, please use this
  document in accordance with the terms of the agreement. If not, please
  destroy the document.}\\[.5ex]

}
\pagebreak
